---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---

We're going to make some plotly plots.

## Load packages and data

```{r}
library(tidyverse)
library(p8105.datasets)

library(plotly)
```

Let's get some data.

```{r}
data("nyc_airbnb")

# narrow down data
nyc_airbnb <-
  nyc_airbnb %>% 
  mutate(rating = review_scores_location / 2) %>% 
  select(
    borough = neighbourhood_group, neighbourhood, price, room_type, lat, long, rating
  ) %>% 
  filter(
    borough == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500
  ) %>% 
  drop_na(rating)
```

Let's make a scatterplot!!

```{r}
nyc_airbnb %>% 
  mutate(
    text_label = str_c("Price: ", price)
  ) %>% 
  plot_ly( 
    x = ~lat, y = ~long, color = ~price,
    type = "scatter", mode = "markers",
    alpha = .5, text = ~text_label
  )
```

Can we make boxplots?? Sure can!

```{r}
nyc_airbnb %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  plot_ly(
    y = ~price, color = ~neighbourhood, 
    type = "box", colors = "viridis"
  )
```

Can we make a bar plot?

```{r}
nyc_airbnb %>% 
  count(neighbourhood) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) %>%
  plot_ly(
    x = ~neighbourhood, y = ~n,
    type =
  )
```

Plotly r graphing library = great place to find different plots


## ggplotly...

```{r}
ggp_scatterplot <- 
  nyc_airbnb %>% 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()

ggplotly(ggp_scatterplot)
```

Helpful to know exist -- it's quicker and easier to make things in ggplot

Problem -- the plots that are made in this way are slower to interact, more difficult to control, less appealing to users

Don't encourage to use
